The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-20 paper/ms.tex
update

\subsubsection{Light curve noise properties}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} 
  The minimum RMS across all three
  aperture sizes was selected.  The photon and read noise are
  calculated using the effective area from \citet{vanderspek_2018}.
  The noise from unresolved background stars is a function of
  galactic latitude, and dominates over zodiacal light and read noise
  for faint stars near the galactic plane; the dotted line assumes a
  sight-line towards the center of Sector 6, Camera 1 (further details
  are in \S~\ref{subsec:lcstatistics}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

>>>>

\subsubsection{Light curve noise properties}
\label{subsubsec:rmsvsmag}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} 
  Black points correspond to the minimum RMS across the available three
  aperture sizes.  
  The model (orange and gray lines) uses the optimal aperture sizes reported 
  by \citet{Sullivan_et_al_2015}, and the effective area from 
  \citet{vanderspek_2018}.
  The noise from unresolved background stars (dotted gray line) is a function 
  of galactic latitude, and dominates over zodiacal light and read noise
  for faint stars near the galactic plane; the line shown assumes a
  sight-line towards the center of Sector 6, Camera 1 (further details
  are in \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}
